Mutual Information Plots

### 2025-10-17 mutual_information_curves.qmd
more changes

  summ <- 0
  for (i in 1:n) {
    for (j in 1:n) {
      if (i != j) {
        summ <- summ + w[i, j] * sign(i - j) * sign(rhat[i] - rhat[j])
        print(summ)
      }

@@

  out <- summ / (sum(w) - sum(diag(w)))
  weight <- (out + 1) / 2
  print(sum(w))
  print(sum(diag(w)))
  return(weight)

@@

@@

  # Weighted Kendall (using provided function)
  kendall_results <- sapply(perms_list, function(p) {
    weighted_kendall(rhat = p, k = 4, wtype = "symmetric_salience")
  })

>>>>

  summ <- 0
  for (i in 1:n) {
    for (j in 1:n) {
      if (i != j) {
        summ <- summ + w[i, j] * sign(i - j) * sign(rhat[i] - rhat[j])
        #print(summ)
      }

@@

  out <- summ / (sum(w) - sum(diag(w)))
  weight <- (out + 1) / 2
  #print(sum(w))
  #print(sum(diag(w)))
  return(weight)

@@

perms_list <- permn(1:4)

@@

  # Weighted Kendall (using provided function)
  kendall_results <- sapply(perms_list, function(p) {
    weighted_kendall(rhat = p, k = k, wtype = "symmetric_salience")
  })
